Hydras \& Co.

### 2022-03-10 doc/chapter-powers.tex
small changes
new title page
Fix a few (too long to generate) snippets

\index{coq}{Coercions}

@@

\inputsnippets{Addition_Chains/slowC87Correct}

@@

\index{coq}{Plug-ins!paramcoq}

@@

\begin{Coqbad}
Module Bad.

Definition Fchain_correct  (n:nat) (f : Fchain) :=
  forall A `(M : @EMonoid A op E_one E_equiv) k (a:A),
    computation_execute op (f A k  a)==
    computation_execute op (k  (a ^ n)).
\end{Coqbad}

@@

\inputsnippets{Euclidean_Chains/BadDefa}
\inputsnippets{Euclidean_Chains/BadDefb}

@@

\begin{Coqsrc}
Definition fib_eucl gamma `{Hgamma: Strategy gamma} n :=
  let c := make_chain gamma  n
  in let r := chain_apply c (M:=Mul2) (1,0) in
       fst r + snd r.

Compute fib_eucl dicho 153.
\end{Coqsrc}

\begin{Coqanswer}
    = 68330027629092351019822533679447
     : N
Finished transaction in 0.002 secs (0.002u,0.s) (successful)
\end{Coqanswer}

\begin{Coqsrc}
Compute fib_eucl two 153.
\end{Coqsrc}

\begin{Coqanswer}
    = 68330027629092351019822533679447
     : N
Finished transaction in 0.003 secs (0.003u,0.s) (successful)
\end{Coqanswer}

\begin{Coqsrc}
Compute fib_eucl half 153.
\end{Coqsrc}

\begin{Coqanswer}
    = 68330027629092351019822533679447
     : N
Finished transaction in 0.003 secs (0.003u,0.s) (successful)
\end{Coqanswer}

>>>>

@@

\begin{Coqbad}
Example C87_ok_slow : chain_correct 87 C87.
Proof.
Time slow_chain_correct_tac.
\end{Coqbad}

\begin{Coqanswer}
Finished transaction in 49.927 secs (49.445u,0.079s) (successful)
\end{Coqanswer}

\begin{Coqbad}
Qed.
\end{Coqbad}

%\inputsnippets{Addition_Chains/slowC87Correct}

@@

\index{coq}{Plug-ins!Paramcoq}

@@

\inputsnippets{Euclidean_Chains/BadDefa}

@@

\inputsnippets{Euclidean_Chains/BadDefb}

@@

\inputsnippets{Fib2/fibEuclDemo}

### 2022-03-10 doc/hydras.tex
first try
failed attempt to generate snippets with utf8 characters
utf8 omega accepted
try to use DejaVu Sans Mono
add a few lemmas
Bridge dev (#112)
* more lemmas (draft)

* add a type E0 (in Bridge)

* experiments in bridge building

* experiments in bridge building

* experiments in bridge building

* fix a typo in gaia-chapter.tex

* fix a typo in gaia-chapter.tex

* first try

* failed attempt to generate snippets with utf8 characters

* additions to GCanon.V

* utf8 omega accepted

* Canonical sequences in Bridge (initial)

* try to use DejaVu Sans Mono

* add a few lemmas

* fix a typo

\documentclass[twoside,a4paper]{book}
\usepackage{alltt}
\usepackage{multind}
\usepackage{hyperref}
\usepackage{url}
\usepackage{xcolor, fancyvrb, mdframed}
\usepackage{amsmath}
%\usepackage{fancyhdr}
\usepackage{varioref}
\usepackage{synttree, proof, centernot}
%\usepackage[firstpage]{draftwatermark}
\usepackage{verbatim}
\usepackage[note]{marginote}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{float}
\usepackage{threeparttable}
\usepackage{fontspec}
\usepackage{mathtools}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{placeins}
\usepackage{tikz}
\usepackage{tikzsymbols}
\usetikzlibrary{arrows}
\usepackage{graphicx}
\usepackage{amsmath,mathdots,dsfont}
\usepackage{amssymb}
\usepackage{newunicodechar}
\usepackage{theorem}
\usepackage{xspace}
\usepackage{texments}
%%% for movies by alectryon
\usepackage{movies/snippets/assets/alectryon}
\usepackage{movies/snippets/assets/pygments}

@@

\clearpage
\newpage
% \mbox{~}
\begin{quote}
 \emph{(Aprieta el bast\'on con las dos manos, se yergue un tanto,
casi con entusiasmo)} ¡Caramba! Claro \dots{} los n\'umeros
transfinitos, Kantor \dots{}

[ Jorge Luis Borges]
\end{quote}
\vspace{2cm}
\begin{quote}
  Nessun senso percepisce l'infinito. Nessun senso permette di concludere ch'esso esista. L'infinito, in effetti, non puo' essere l'oggetto dei sensi.

@@

\vspace{2cm}
\begin{quote} 
I start from one point and go as far as possible.

[John Coltrane]
\end{quote}

@@

\subsubsection{Using \alectr}

Here is an example from Chapter~\ref{chapter:primrec}.

@@

@@

\begin{Coqsrc}
Definition fib_eucl gamma `{Hgamma: Strategy gamma} n :=
  let c := make_chain gamma  n
  in let r := chain_apply c (M:=Mul2) (1,0) in
       fst r + snd r.

Compute fib_eucl dicho 153.
\end{Coqsrc}

\begin{Coqanswer}
    = 68330027629092351019822533679447
     : N
\end{Coqanswer}

@@

@@

\include{part-hydras}
\include{chapter-primrec}
\include{gaia-chapter}
\part{A few  certified algorithms}

>>>>

\documentclass[twoside,a4paper]{book}

%\usepackage{fontenc}
\usepackage[utf8x]{inputenc}

\usepackage{fontspec}
%\setmainfont{DejaVu Serif}

\setmonofont{DejaVu Sans Mono}[Scale=MatchLowercase]
\usepackage{alltt}
\usepackage{multind}
\usepackage{hyperref}
\usepackage{url}
\usepackage{xcolor, fancyvrb, mdframed}
\usepackage{amsmath}
%\usepackage{fancyhdr}
\usepackage{varioref}
\usepackage{synttree, proof, centernot}
%\usepackage[firstpage]{draftwatermark}
\usepackage{verbatim}
\usepackage[note]{marginote}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathtools}
\usepackage{dsfont}
\usepackage{float}
\usepackage{threeparttable}
\usepackage{fontspec}
\usepackage{mathtools}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{placeins}
\usepackage{tikz}
\usepackage{tikzsymbols}
\usetikzlibrary{arrows}
\usepackage{graphicx}
\usepackage{amsmath,mathdots,dsfont}
\usepackage{amssymb}
\usepackage{newunicodechar}
\usepackage{theorem}
\usepackage{xspace}
\usepackage{texments}
%%% for movies by alectryon
\usepackage{movies/snippets/assets/alectryon}
\usepackage{movies/snippets/assets/pygments}

@@

\clearpage
\newpage
\thispagestyle{empty}
\begin{quote}
 \emph{(Aprieta el bast\'on con las dos manos, se yergue un tanto,
casi con entusiasmo)} ¡Caramba! Claro \dots{} los n\'umeros
transfinitos, Kantor \dots{}

[ Jorge Luis Borges]
\end{quote}
\vspace{17mm}
\begin{quote}
  Nessun senso percepisce l'infinito. Nessun senso permette di concludere ch'esso esista. L'infinito, in effetti, non puo' essere l'oggetto dei sensi.

@@

\vspace{17mm}
\begin{quote} 
I start from one point and go as far as possible.

[John Coltrane]
\end{quote}
\mbox{}
\newpage
\newpage
% \mbox{~}
\thispagestyle{empty}
\label{watercolor}
 {\centering
      \includegraphics[width=13cm]{blue-hydra.jpg}
      \centerline{\emph{``The blue hydra'': Watercolor  by Pierrette Cassou-Noguès}}
}

@@

\subsubsection{Using \alectr}
Whenever possible, we use \alectr to display \coq code (definition, proof scripts) and answers.

Here are two  examples from Chapters~\ref{chapter:primrec}
and~\ref{chapter-powers}.

@@

\inputsnippets{Fib2/fibEuclDemo}

@@

\begin{Coqbad}
Example C87_ok_slow : chain_correct 87 C87.
Proof.
Time slow_chain_correct_tac.
\end{Coqbad}

\begin{Coqanswer}
Finished transaction in 49.927 secs (49.445u,0.079s) (successful)
\end{Coqanswer}

\begin{Coqbad}
Qed.
\end{Coqbad}

@@

Last but not least, many thanks to Pierrette Cassou-Noguès for the watercolor on page~\pageref{watercolor}.

@@

\include{part-hydras}
\include{chapter-primrec}
\part{A few  certified algorithms}
